Counting And Confusion: Bayesian Rate Estimation With Multiple Populations

### 2014-12-11 many.tex
Updates to address referee B's comments.

{\bf Our key results appear in Eq.~(\ref{eq:posterior}), which provides the joint posterior probability distribution on the foreground and background rates and shape parameters and the provenance of individual events as either foreground or background.  Eq.~(\ref{eq:rate-shape-posterior}) is a marginalized version of Eq.~(\ref{eq:posterior}), useful when the provenance of individual events is not relevant.  In practice, these posteriors are best sampled with stochastic techniques such as Markov chain Monte Carlo.}

@@

We assume that both the foreground and background events are samples
from an inhomogeneous Poisson process with respective differential
rates
\begin{equation}
  \frac{dN_f}{dx} = f(x, \theta)
\end{equation}
and
\begin{equation}
  \frac{dN_b}{dx} = b(x, \theta),
\end{equation}
where the $\theta$ argument represents additional ``shape'' parameters
that may affect the distribution, and for which we will eventually
fit.  The cumulative rates of the two processes are therefore
\begin{equation}
  F(x,\theta) \equiv \int_{-\infty}^x ds\, f(s, \theta)
\end{equation}
and
\begin{equation}
  B(x,\theta) \equiv \int_{-\infty}^x ds\, b(s,\theta).
\end{equation}
The assumption that the foreground and background events form an
inhomogeneous Poisson process implies
\begin{enumerate}
\item \label{prop:Poisson} The number of events in any range of
  ranking statistics, $x \in [x_1, x_2]$ is Poisson distributed with
  rate $F(x_2, \theta) - F(x_1,\theta)$ or $B(x_2,\theta) -
  B(x_1,\theta)$.
\item The numbers of events in non-overlapping ranges of ranking
  statistics are independent.
\item The probability of exactly one foreground event between $x$ and
  $x+h$ is given by
  \begin{equation}
    P(n = 1 \in [x, x+h]) = f(x,\theta) h + \order{h^2}.
  \end{equation}
  and similarly for background events.
\item The probability of two or more events in a small range of
  ranking statistic is negligible
  \begin{equation}
    P(n = 2 \in [x, x+h]) = \order{h^2}.
  \end{equation}
\end{enumerate}
The foreground and background rates can in general depend on several
parameters; the goal of our analysis is to determine the posterior
probability distributions for these parameters that are implied by the
data.  At the least, we will want to know the overall {\bf dimensionless} 
amplitude of the foreground and background rates.  Let
\begin{equation}
  f(x,\theta) = R_f \hat{f}(x,\theta'),
\end{equation}
and
\begin{equation}
  b(x, \theta) = R_b \hat{b}(x, \theta'),
\end{equation}
where $\hat{F}(\infty, \theta') = \hat{B}(\infty, \theta') = 1$, and
$\theta' = \theta \setminus \{R_{f}, R_{b} \}$.  Then $R_f \equiv
F(\infty,\theta)$ and $R_b \equiv B(\infty,\theta)$ are the total
number of foreground and background events expected and $\hat{f}(x,
\theta')$ and $\hat{b}(x, \theta')$ are the likelihood of obtaining an
event with ranking statistic $x$ under the foreground and background
distributions.  In what follows, we will drop the prime, using
$\theta$ to denote all parameters of the rate distributions except
$R_f$ and $R_b$.

@@

{\bf This problem can also be avoided
in the context of the loudest-event framework by even very weak prior
information on the background rate, $R_b$, of the kind present in
nearly all experiments.  For example, we can include an upper limit
on the rate, $R_{\rm max}$, in the prior for $R_b$.}
\begin{widetext}
The marginalized distribution for the foreground rate then becomes
\begin{eqnarray}
p_{\rm LE}\left( R_f, \theta | d \right) &\propto& \left(
\frac{\hat{b}(x_N,\theta)}{(1-\hat{B}(x_N,\theta))^{\frac{3}{2}}}
\left[\frac{\sqrt{\pi}}{2}{\rm
    erf}\left(\sqrt{(1-\hat{B}(x_N,\theta))\,R_{\rm max}}\right) -
  \sqrt{(1-\hat{B}(x_N,\theta))\,R_{\rm max}} \, {\rm
    e}^{-(1-\hat{B}(x_N,\theta)) \, R_{\rm max}}\right]
\right. \nonumber \\ && \left.+ R_f
\hat{f}(x_N,\theta)\frac{\sqrt{\pi}\,{\rm
    erf}\left(\sqrt{(1-\hat{B}(x_N,\theta))\,R_{\rm
      max}}\right)}{\sqrt{(1-\hat{B}(x_N,\theta))}}\right)\frac{p(\theta)}{\sqrt{R_f}}
\exp\left(-R_f(1-\hat{F}(x_N,\theta))\right) \label{LEwithRmax},
\end{eqnarray}
where ${\rm erf}(x)$ is the error function, defined in the usual way
${\rm erf}(x) = (2/\sqrt{\pi}) \int_0^x \exp(-u^2){\rm d}u$. If
$(1-\hat{B}(x_N,\theta)) \, R_{\rm max} \ll 1$, Eq.~(\ref{LEwithRmax})
can be approximated by
\begin{equation}
p_{\rm LE}\left( R_f, \theta | d \right) \propto \left( \frac{R_{\rm
    max}}{3} \hat{b}(x_N,\theta) + R_f
\hat{f}(x_N,\theta)\right)\frac{p(\theta)}{\sqrt{R_f}}
\exp\left(-R_f(1-\hat{F}(x_N,\theta))\right)
\end{equation}
and if $\hat{f}(x_N,\theta) \gg R_{\rm max} \hat{b}(x_N,\theta)$ we
find the same result as before, $(1- \hat{F}(x_N,\theta))\,R_f \approx
1/2$.
\end{widetext}

\subsection{Foreground dominated statistic}
If we set the threshold for including an event, $x_{\rm min}$,
sufficiently high, we can ensure that $\hat{f}(x_i,\theta) \gg
\hat{b}(x_i,\theta)$ for all ranking statistics $x_i$ in the data
set.  If we can further be confident that $R_f \hat{f}(x_i,\theta) \gg R_b \hat{b}(x_i,\theta)$ for all events, then the posterior can be approximated by
\begin{multline}
p_{\rm FD}\left( R_f, R_b, \theta | d \right) \\ \propto \prod_{i} \left[
  \hat{f}\left(x_i, \theta\right)\right] R_f^N \exp\left[-\left( R_f +
  R_b \right) \right] \frac{p(\theta)}{\sqrt{R_f R_b}}.
\end{multline}
Note that these are posteriors on the number of events expected \emph{above the
threshold $x_{\rm min}$}.  The threshold choice for the foreground-dominated statistic could be different from the threshold choice applied elsewhere.  
%If rates $R_{f,1}$ and $R_{f,2}$ are estimated for thresholds $x_{\rm min}=x_1$, $x_{\rm min}=x_2$ respectively, these rates should be compared by equating $R_{f,1} (1-\hat{F}(x_2,\theta))$ and $R_{f,2} (1-\hat{F}(x_1,\theta))$.
{\bf If the rates are estimated accurately, then a rate estimate $R_{f,1}$ above threshold $x_{\rm min}=x_1$ can be converted into a rate estimate $R_{f,2}$ above threshold $x_{\rm min}=x_2$ via 
$R_{f,1} (1-\hat{F}(x_2,\theta)) = R_{f,2} (1-\hat{F}(x_1,\theta))$; however, rate point estimates based on thresholding can have significant fluctuations, as discussed in the following section.}

@@

To begin with, we recall the well-known fact that the Bayesian
estimator is unbiased, in the following sense.  For simplicity, assume
that the model consists of a single rate parameter $R$, with prior
distribution $p(R)$.  Consider an ensemble of data sets whose
distribution is consistent with that prior; i.e., such that $p(d)$ is
given by
%Construct and ensemble of synthetic data sets consistent with $p(R)$; i.e., draw data from the %distribution
\begin{equation}
 p(d) = \int{ p(d|R)\,p(R)\, dR}\, .  
\end{equation}
For each data set in the ensemble, compute the Bayesian estimator 
for the mean of the posterior $R_{B} = \int{ R p(R|d) dR}$.  Then it is immediate that
\begin{equation}
\int{R_{B}(d)\, p(d)\,d(d) }= \int{ R\, p(R) \,dR},
\end{equation}
i.e.\ the data-weighted average of the Bayesian {\bf estimator} $R_{B}$
equals the prior-weighted average $R$.  Therefore all threshold values
will yield, on average, the same {\bf point} estimate of the rate.  However this
equality of averages does {\it not} imply that all threshold values
yield the same information. In general, as the threshold is lowered to
include more events, the error bar on the estimate shrinks.  In this
subsection we give quantitative illustrations of how the error bar
shrinks when the threshold is lowered.

@@

Though we have only illustrated the behavior of the rate estimate
quantitatively for this specific example of foreground and background
rates, the conclusions hold in general.  Consider the Fisher
information matrix for the posterior distribution in
Eq.~\eqref{eq:rate-shape-posterior}.  For a model with parameters
$\mathset{\theta_i}$, the Fisher information matrix has components
\begin{equation}
  F_{ij} \equiv \left\langle \frac{\partial \log p\left( \theta | d
    \right)}{\partial \theta_i} \frac{\partial \log p\left( \theta | d
    \right)}{\partial \theta_j} \right\rangle,
\end{equation}
where the average is taken over the data distribution at fixed
$\theta$, $p(d | \theta)$.  The components of the Fisher information
matrix describe the maximum amount of information about the
corresponding parameters available in a given data set; the inverse of
the Fisher information matrix gives the Cramer-Rao bound on the
covariance matrix of unbiased estimators of $\theta$.  For the
likelihood that enters Eq.~\eqref{eq:rate-shape-posterior}, the Fisher
information matrix is 
\begin{multline}
  \mathbf{F} = \left( R_f + R_b \right) \\ \times \begin{pmatrix}
    \left \langle \left(\frac{\hat{f}}{R_f \hat{f} + R_b \hat{b}}\right)^2 \right
    \rangle & \left \langle \frac{\hat{f} \hat{b}}{\left( R_f \hat{f}
      + R_b \hat{b} \right)^2} \right\rangle \\
    \left \langle \frac{\hat{f} \hat{b}}{\left( R_f \hat{f}
      + R_b \hat{b} \right)^2} \right\rangle & \left \langle
    \left(\frac{\hat{b}}{R_f \hat{f} + R_b \hat{b}}\right)^2 \right 
    \rangle
  \end{pmatrix},
\end{multline}
where the expectation values are taken over the distributions
$\hat{f}$ and $\hat{b}$ (i.e.\ they are expectations for one event
from the combined rate distribution).  If the cross-terms are small,
then the Cramer-Rao bound on the uncertainty of $R_f$ will be given by
\begin{equation}
  \sigma_{R_f} \simeq \frac{1}{\sqrt{R_f + R_b}} \left[ \left\langle \left(
    \frac{\hat{f}}{R_f \hat{f} + R_b \hat{b}} \right)^2 \right\rangle\right]^{-1/2}
\end{equation}
Extending a threshold into regions where the factor 
\begin{equation}
  \left( \frac{\hat{f}}{R_f \hat{f} + R_b \hat{b}} \right)^2
\end{equation}
becomes small---that is, into background-dominated
regions---contributes little to reducing the overall uncertainty in the
foreground rate.  Thus, when the background distribution itself is of no interest and computational costs are high, the threshold does not need to be pushed into background-dominated regions in order to obtain an accurate foreground estimate. This is consistent with the behavior of the specific
example in Figure \ref{fig:threshold-rate-dependence}.

@@

If we consider the two alternative methods, the loudest event and
foreground dominated statistics, and apply the same
foreground-dominated thresholds as before, we will recover the same
foreground distributions as are shown in Figure~\ref{fig:altmeth}.
This is because the parameter $N_{\rm eff}$ affects only the
background distribution, to which the foreground-dominated statistic
is insensitive, and in the loudest event case, after marginalization
over $N_{\rm eff}$ we find $\int_0^{N_{\rm max}} \hat{b}(x_N,N_{\rm
  eff}) {\rm d}N_{\rm eff} \ll 3 N_{\rm max}/R_{\rm max} \hat{f}(x_N,
N_{\rm eff})$ and so we are still in the foreground-dominated regime
in which the loudest event tells us nothing about the background.
Neither of these alternative methods can inform us about the value of
$N_{\rm eff}$, a {\bf property of the distribution of background events identified by filtering with this template bank}.  Moreover, the choice of
threshold value for the foreground-dominated statistic becomes
significantly more complicated in this case, since $p_\mathrm{thresh}$
now depends on $N_\mathrm{eff}$.

@@

Figure \ref{fig:cluster-params} shows the posteriors for the cluster
parameters.  The center of the cluster, $\vec{x}_0$, is localized to
within about 5\% of the cluster scale, and the cluster radius with a
relative error of about 10\%.  In spite of the significant background,
the cluster parameters are recovered to a relative accuracy consistent
with the expected uncertainty from $N_\mathrm{eff} \simeq R_f = 1000$
measurements.  Figure \ref{fig:cluster-number} shows the posteriors
inferred on the cluster and background numbers, $R_f$ and $R_b$.

\begin{figure}
  \includegraphics[width=0.475\columnwidth]{sky_location}\includegraphics[width=0.475\columnwidth]{scale}
  \caption{\label{fig:cluster-params} Posterior density for the
    cluster parameters for the example from \S~\ref{sec:star-cluster}.
    (Left) Contours of the posterior probability distribution for the
    center of the cluster, $\vec{x}_0$.  The center $(x,y) =
    \left(x_0, y_0\right)$ is determined to within about 5\% of the
    structural radius of the cluster, $r_0$ (see
    Eq.~\eqref{eq:true-cluster-parameters}).  (Right) Posterior
    density for the scale parameter for the cluster, $r_0$.  The true
    value is indicated by the vertical line (see
    Eq.~\ref{eq:true-cluster-parameters}).}
\end{figure}

>>>>

Our key results appear in Eq.~(\ref{eq:posterior}), which provides the
joint posterior probability distribution on the foreground and
background rates and shape parameters and the provenance of individual
events as either foreground or background.
Eq.~(\ref{eq:rate-shape-posterior}) is a marginalized version of
Eq.~(\ref{eq:posterior}), useful when the provenance of individual
events is not relevant.  In practice, these posteriors are best
sampled with stochastic techniques such as Markov chain Monte Carlo.

@@

We assume that both the foreground and background events are samples
from an inhomogeneous Poisson process with respective differential
rates
\begin{equation}
  \frac{dN_f}{dx} = f(x, \theta)
\end{equation}
and
\begin{equation}
  \frac{dN_b}{dx} = b(x, \theta),
\end{equation}
where the $\theta$ argument represents additional ``shape'' parameters
that may affect the distribution, and for which we will eventually
fit.  The cumulative rates of the two processes are therefore
\begin{equation}
  F(x,\theta) \equiv \int_{-\infty}^x ds\, f(s, \theta)
\end{equation}
and
\begin{equation}
  B(x,\theta) \equiv \int_{-\infty}^x ds\, b(s,\theta).
\end{equation}
The assumption that the foreground and background events form an
inhomogeneous Poisson process implies
\begin{enumerate}
\item \label{prop:Poisson} The number of events in any range of
  ranking statistics, $x \in [x_1, x_2]$ is Poisson distributed with
  rate $F(x_2, \theta) - F(x_1,\theta)$ or $B(x_2,\theta) -
  B(x_1,\theta)$.
\item The numbers of events in non-overlapping ranges of ranking
  statistics are independent.
\item The probability of exactly one foreground event between $x$ and
  $x+h$ is given by
  \begin{equation}
    P(n = 1 \in [x, x+h]) = f(x,\theta) h + \order{h^2}.
  \end{equation}
  and similarly for background events.
\item The probability of two or more events in a small range of
  ranking statistic is negligible
  \begin{equation}
    P(n = 2 \in [x, x+h]) = \order{h^2}.
  \end{equation}
\end{enumerate}
The foreground and background rates can in general depend on several
parameters; the goal of our analysis is to determine the posterior
probability distributions for these parameters that are implied by the
data.  At the least, we will want to know the overall dimensionless
amplitude of the foreground and background rates.  Let
\begin{equation}
  f(x,\theta) = R_f \hat{f}(x,\theta'),
\end{equation}
and
\begin{equation}
  b(x, \theta) = R_b \hat{b}(x, \theta'),
\end{equation}
where $\hat{F}(\infty, \theta') = \hat{B}(\infty, \theta') = 1$, and
$\theta' = \theta \setminus \{R_{f}, R_{b} \}$.  Then $R_f \equiv
F(\infty,\theta)$ and $R_b \equiv B(\infty,\theta)$ are the total
number of foreground and background events expected and $\hat{f}(x,
\theta')$ and $\hat{b}(x, \theta')$ are the likelihood of obtaining an
event with ranking statistic $x$ under the foreground and background
distributions.  In what follows, we will drop the prime, using
$\theta$ to denote all parameters of the rate distributions except
$R_f$ and $R_b$.

@@

This problem can also be avoided in the context of the loudest-event
framework by even very weak prior information on the background rate,
$R_b$, of the kind present in nearly all experiments.  For example, we
can include an upper limit on the rate, $R_{\rm max}$, in the prior
for $R_b$.
\begin{widetext}
The marginalized distribution for the foreground rate then becomes
\begin{eqnarray}
p_{\rm LE}\left( R_f, \theta | d \right) &\propto& \left(
\frac{\hat{b}(x_N,\theta)}{(1-\hat{B}(x_N,\theta))^{\frac{3}{2}}}
\left[\frac{\sqrt{\pi}}{2}{\rm
    erf}\left(\sqrt{(1-\hat{B}(x_N,\theta))\,R_{\rm max}}\right) -
  \sqrt{(1-\hat{B}(x_N,\theta))\,R_{\rm max}} \, {\rm
    e}^{-(1-\hat{B}(x_N,\theta)) \, R_{\rm max}}\right]
\right. \nonumber \\ && \left.+ R_f
\hat{f}(x_N,\theta)\frac{\sqrt{\pi}\,{\rm
    erf}\left(\sqrt{(1-\hat{B}(x_N,\theta))\,R_{\rm
      max}}\right)}{\sqrt{(1-\hat{B}(x_N,\theta))}}\right)\frac{p(\theta)}{\sqrt{R_f}}
\exp\left(-R_f(1-\hat{F}(x_N,\theta))\right) \label{LEwithRmax},
\end{eqnarray}
where ${\rm erf}(x)$ is the error function, defined in the usual way
${\rm erf}(x) = (2/\sqrt{\pi}) \int_0^x \exp(-u^2){\rm d}u$. If
$(1-\hat{B}(x_N,\theta)) \, R_{\rm max} \ll 1$, Eq.~(\ref{LEwithRmax})
can be approximated by
\begin{equation}
p_{\rm LE}\left( R_f, \theta | d \right) \propto \left( \frac{R_{\rm
    max}}{3} \hat{b}(x_N,\theta) + R_f
\hat{f}(x_N,\theta)\right)\frac{p(\theta)}{\sqrt{R_f}}
\exp\left(-R_f(1-\hat{F}(x_N,\theta))\right)
\end{equation}
and if $\hat{f}(x_N,\theta) \gg R_{\rm max} \hat{b}(x_N,\theta)$ we
find the same result as before, $(1- \hat{F}(x_N,\theta))\,R_f \approx
1/2$.
\end{widetext}

\subsection{Foreground dominated statistic}
If we set the threshold for including an event, $x_{\rm min}$,
sufficiently high, we can ensure that $\hat{f}(x_i,\theta) \gg
\hat{b}(x_i,\theta)$ for all ranking statistics $x_i$ in the data
set.  If we can further be confident that $R_f \hat{f}(x_i,\theta) \gg R_b \hat{b}(x_i,\theta)$ for all events, then the posterior can be approximated by
\begin{multline}
p_{\rm FD}\left( R_f, R_b, \theta | d \right) \\ \propto \prod_{i} \left[
  \hat{f}\left(x_i, \theta\right)\right] R_f^N \exp\left[-\left( R_f +
  R_b \right) \right] \frac{p(\theta)}{\sqrt{R_f R_b}}.
\end{multline}
Note that these are posteriors on the number of events expected \emph{above the
threshold $x_{\rm min}$}.  The threshold choice for the foreground-dominated statistic could be different from the threshold choice applied elsewhere.  
%If rates $R_{f,1}$ and $R_{f,2}$ are estimated for thresholds $x_{\rm min}=x_1$, $x_{\rm min}=x_2$ respectively, these rates should be compared by equating $R_{f,1} (1-\hat{F}(x_2,\theta))$ and $R_{f,2} (1-\hat{F}(x_1,\theta))$.
If the rates are estimated accurately, then a rate estimate $R_{f,1}$
above threshold $x_{\rm min}=x_1$ can be converted into a rate
estimate $R_{f,2}$ above threshold $x_{\rm min}=x_2$ via $R_{f,1}
(1-\hat{F}(x_2,\theta)) = R_{f,2} (1-\hat{F}(x_1,\theta))$; however,
rate point estimates based on thresholding can have significant
fluctuations, as discussed in the following section.

@@

To begin with, we recall the well-known fact that the Bayesian
estimator is unbiased, in the following sense.  For simplicity, assume
that the model consists of a single rate parameter $R$, with prior
distribution $p(R)$.  Consider an ensemble of data sets whose
distribution is consistent with that prior; i.e., such that $p(d)$ is
given by
%Construct and ensemble of synthetic data sets consistent with $p(R)$; i.e., draw data from the %distribution
\begin{equation}
 p(d) = \int{ p(d|R)\,p(R)\, dR}\, .  
\end{equation}
For each data set in the ensemble, compute the Bayesian estimator 
for the mean of the posterior $R_{B} = \int{ R p(R|d) dR}$.  Then it is immediate that
\begin{equation}
\int{R_{B}(d)\, p(d)\,d(d) }= \int{ R\, p(R) \,dR},
\end{equation}
i.e.\ the data-weighted average of the Bayesian estimator $R_{B}$
equals the prior-weighted average $R$.  Therefore all threshold values
will yield, on average, the same point estimate of the rate.  However
this equality of averages does {\it not} imply that all threshold
values yield the same information. In general, as the threshold is
lowered to include more events, the error bar on the estimate shrinks.
In this subsection we give quantitative illustrations of how the error
bar shrinks when the threshold is lowered.

@@

Though we have only illustrated the behavior of the rate estimate
quantitatively for this specific example of foreground and background
rates, the conclusions hold in general.  Consider the Fisher
information matrix for the posterior distribution in
Eq.~\eqref{eq:rate-shape-posterior}.  For a model with parameters
$\mathset{\theta_i}$, the Fisher information matrix has components
\begin{equation}
  F_{ij} \equiv \left\langle \frac{\partial \log p\left( \theta | d
    \right)}{\partial \theta_i} \frac{\partial \log p\left( \theta | d
    \right)}{\partial \theta_j} \right\rangle,
\end{equation}
where the average is taken over the data distribution at fixed
$\theta$, $p(d | \theta)$.  The components of the Fisher information
matrix describe the maximum amount of information about the
corresponding parameters available in a given data set; the inverse of
the Fisher information matrix gives the Cramer-Rao bound on the
covariance matrix of unbiased estimators of $\theta$.  Though our
Bayesian analysis is not necessarily limited by the Cramer-Rao bound
(since estimators constructed from it need not be unbiased and can
also be affected by the prior), the Fisher information is indicative
of the influence of each measurement on the posterior.  For the
likelihood that enters Eq.~\eqref{eq:rate-shape-posterior}, the Fisher
information matrix is
\begin{multline}
  \mathbf{F} = \left( R_f + R_b \right) \\ \times \begin{pmatrix}
    \left \langle \left(\frac{\hat{f}}{R_f \hat{f} + R_b \hat{b}}\right)^2 \right
    \rangle & \left \langle \frac{\hat{f} \hat{b}}{\left( R_f \hat{f}
      + R_b \hat{b} \right)^2} \right\rangle \\
    \left \langle \frac{\hat{f} \hat{b}}{\left( R_f \hat{f}
      + R_b \hat{b} \right)^2} \right\rangle & \left \langle
    \left(\frac{\hat{b}}{R_f \hat{f} + R_b \hat{b}}\right)^2 \right 
    \rangle
  \end{pmatrix},
\end{multline}
where the expectation values are taken over the distributions
$\hat{f}$ and $\hat{b}$ (i.e.\ they are expectations for one event
from the combined rate distribution).  If the cross-terms are small,
then the Cramer-Rao bound on the uncertainty of $R_f$ will be given by
\begin{equation}
  \sigma_{R_f} \simeq \frac{1}{\sqrt{R_f + R_b}} \left[ \left\langle \left(
    \frac{\hat{f}}{R_f \hat{f} + R_b \hat{b}} \right)^2 \right\rangle\right]^{-1/2}
\end{equation}
Extending a threshold into regions where the factor 
\begin{equation}
  \left( \frac{\hat{f}}{R_f \hat{f} + R_b \hat{b}} \right)^2
\end{equation}
becomes small---that is, into background-dominated
regions---contributes little to reducing the overall uncertainty in the
foreground rate.  Thus, when the background distribution itself is of no interest and computational costs are high, the threshold does not need to be pushed into background-dominated regions in order to obtain an accurate foreground estimate. This is consistent with the behavior of the specific
example in Figure \ref{fig:threshold-rate-dependence}.

@@

If we consider the two alternative methods, the loudest event and
foreground dominated statistics, and apply the same
foreground-dominated thresholds as before, we will recover the same
foreground distributions as are shown in Figure~\ref{fig:altmeth}.
This is because the parameter $N_{\rm eff}$ affects only the
background distribution, to which the foreground-dominated statistic
is insensitive, and in the loudest event case, after marginalization
over $N_{\rm eff}$ we find $\int_0^{N_{\rm max}} \hat{b}(x_N,N_{\rm
  eff}) {\rm d}N_{\rm eff} \ll 3 N_{\rm max}/R_{\rm max} \hat{f}(x_N,
N_{\rm eff})$ and so we are still in the foreground-dominated regime
in which the loudest event tells us nothing about the background.
Neither of these alternative methods can inform us about the value of
$N_{\rm eff}$, a property of the distribution of background events
identified by filtering with this template bank.  Moreover, the choice
of threshold value for the foreground-dominated statistic becomes
significantly more complicated in this case, since $p_\mathrm{thresh}$
now depends on $N_\mathrm{eff}$.

@@

Figures \ref{fig:cluster-loc} and \ref{fig:cluster-scale} shows the
posteriors for the cluster location and scale parameters.  The center
of the cluster, $\vec{x}_0$, is localized to within about 5\% of the
cluster scale, and the cluster radius with a relative error of about
10\%.  In spite of the significant background, the cluster parameters
are recovered to a relative accuracy consistent with the expected
uncertainty from $N_\mathrm{eff} \simeq R_f = 1000$ measurements.
Figure \ref{fig:cluster-number} shows the posteriors inferred on the
cluster and background numbers, $R_f$ and $R_b$.

\begin{figure}
  \includegraphics[width=\columnwidth]{sky_location}
  \caption{\label{fig:cluster-loc} Contours of the posterior
    probability distribution for the center of the cluster,
    $\vec{x}_0$, for the example from \S~\ref{sec:star-cluster}.  The
    center $(x,y) = \left(x_0, y_0\right)$ is determined to within
    about 5\% of the structural radius of the cluster, $r_0$ (see
    Eq.~\eqref{eq:true-cluster-parameters}).}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{scale}
  \caption{\label{fig:cluster-scale} Posterior density for the scale
    parameter for the cluster, $r_0$, for the example from
    \S~\ref{sec:star-cluster}.  The true value is indicated by the
    vertical line (see Eq.~\ref{eq:true-cluster-parameters}).}
\end{figure}
